Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
added field estimation over all time

	\caption{{\bf Actual and estimated spatiotemporal neural field at different spatial resolutions}. (\textbf{A}) The reconstructed field of the reduced model using only scaling functions at $j=0$. (\textbf{B}) The reconstructed field using scaling and wavelet functions at $j=0$. (\textbf{C}) The reconstructed field using scaling and wavelet functions at $j=1$. (\textbf{D}) The reconstructed field using scaling and wavelet functions at $j=2$. (\textbf{E}) The reconstructed field using scaling and wavelet functions at $j=3$. (\textbf{F}) The actual field.}

>>>>

	\caption{{\bf Actual and estimated spatiotemporal neural field at different spatial resolutions}. (\textbf{A}) The reconstructed field of the reduced model using at $j=0$. (\textbf{B}) The reconstructed field at $j=1$. (\textbf{C}) The reconstructed field at $j=2$. (\textbf{D}) The reconstructed field at $j=3$. (\textbf{E}) The reconstructed at $j=4$. (\textbf{F}) The actual field.}
